Global study of well-being and internet adoption | Online analysis supplement

### 2021-11-29 03-model-estimate.Rmd
Don't estimate SE for selfharm

```{r}
# Transform edge proportions to fit beta distribution
# when this is used as an outcome
itu <- itu %>% 
  mutate(ib = if_else(internet == 0, .0000001, internet)) %>% 
  mutate(ib = if_else(internet == 1, .9999999, internet))

# Create lagged predictors
itu <- itu %>% 
  arrange(region, country, year) %>% 
  group_by(region, country) %>% 
  mutate(
    across(
      c(internet, fixed, mobile), 
      list(`1` = ~lag(., 1)), 
      .names = "{str_sub(.col, 1, 1)}{.fn}"
    )
  )

@@

```{r}
fits_1 <- dat %>%
  group_by(cause) %>% 
  summarise(
    fit = list(
      brm(
        formula = bf_itu + bf_1 + set_rescor(FALSE), 
        data = cur_data_all(),
        chains = hmc$chains, 
        cores = hmc$cores, 
        threads = hmc$threads,
        iter = hmc$iter, 
        warmup = hmc$warmup, 
        refresh = hmc$refresh,
        control = list(
          adapt_delta = hmc$adapt_delta, 
          max_treedepth = hmc$max_treedepth
        ),
        file = str_glue("output/brm-1-{cur_group()}")
      )
    )
  )

# fits_1_se <- dat %>%
#   filter(!(cause %in% c("Anxiety", "Depression", "Selfharm")))
#   group_by(cause) %>%
#   summarise(
#     fit_se = list(
#       brm(
#         formula = bf_itu + bf_1_se + set_rescor(FALSE),
#         data = cur_data_all(),
#         chains = hmc$chains,
#         cores = hmc$cores,
#         threads = hmc$threads,
#         iter = hmc$iter,
#         warmup = hmc$warmup,
#         refresh = hmc$refresh,
#         control = list(
#           adapt_delta = hmc$adapt_delta,
#           max_treedepth = hmc$max_treedepth
#         ),
#         file = str_glue("output/brm-1-se-{cur_group()}")
#       )
#     )
#   )
```

@@

# fits_2 <- dat %>%
#   group_by(cause) %>% 
#   summarise(
#     fit_se = list(
#       brm(
#         formula = bf_2_se, 
#         data = cur_data_all(),
#         chains = hmc$chains, 
#         cores = hmc$cores, 
#         threads = hmc$threads,
#         iter = hmc$iter, 
#         warmup = hmc$warmup, 
#         refresh = hmc$refresh,
#         control = list(
#           adapt_delta = hmc$adapt_delta, 
#           max_treedepth = hmc$max_treedepth
#         ),
#         file = str_glue("output/brm-2-se-{cur_group()}")
#       )
#     )
#   )
```

@@

```{r}
bf_2_f <- bf(
  val ~ 
    year * sex + year * age + f1_cw * sex + f1_cw * age + f1_cb + 
    (year * sex + year * age + f1_cw * sex + f1_cw * age | country) +
    (year * sex + year * age + f1_cw * sex + f1_cw * age | region),
  family = gaussian()
)

@@

bf_2_m <- bf(
  val ~ 
    year * sex + year * age + m1_cw * sex + m1_cw * age + m1_cb + 
    (year * sex + year * age + m1_cw * sex + m1_cw * age | country) +
    (year * sex + year * age + m1_cw * sex + m1_cw * age | region),
  family = gaussian()
)

>>>>

```{r}
# Create lagged predictors
itu <- itu %>% 
  arrange(region, country, year) %>% 
  group_by(region, country) %>% 
  mutate(
    across(
      c(internet, fixed, mobile), 
      list(`1` = ~lag(., 1)), 
      .names = "{str_sub(.col, 1, 1)}{.fn}"
    )
  )

@@

```{r}
fits_1 <- dat %>%
  group_by(cause) %>% 
  summarise(
    fit = list(
      brm(
        formula = bf_itu + bf_1 + set_rescor(FALSE), 
        # Transform intrnet edge values
        data = cur_data_all() %>% 
          mutate(internet = if_else(internet == 0, .0000001, internet)) %>% 
          mutate(internet = if_else(internet == 1, .9999999, internet)),
        chains = hmc$chains, 
        cores = hmc$cores, 
        threads = hmc$threads,
        iter = hmc$iter, 
        warmup = hmc$warmup, 
        refresh = hmc$refresh,
        control = list(
          adapt_delta = hmc$adapt_delta, 
          max_treedepth = hmc$max_treedepth
        ),
        file = str_glue("output/brm-1-{cur_group()}")
      )
    )
  )

# This does not converge with selfharm
fits_1_se <- dat %>%
  filter(!(cause %in% c("Selfharm"))) %>% 
  group_by(cause) %>%
  summarise(
    fit_se = list(
      brm(
        formula = bf_itu + bf_1_se + set_rescor(FALSE),
        data = cur_data_all(),
        chains = hmc$chains,
        cores = hmc$cores,
        threads = hmc$threads,
        iter = hmc$iter,
        warmup = hmc$warmup,
        refresh = hmc$refresh,
        control = list(
          adapt_delta = hmc$adapt_delta,
          max_treedepth = hmc$max_treedepth
        ),
        file = str_glue("output/brm-1-se-{cur_group()}")
      )
    )
  )
```

@@

fits_2 <- dat %>%
  filter(!(cause %in% c("Selfharm"))) %>% 
  group_by(cause) %>%
  summarise(
    fit_se = list(
      brm(
        formula = bf_2_se,
        data = cur_data_all(),
        chains = hmc$chains,
        cores = hmc$cores,
        threads = hmc$threads,
        iter = hmc$iter,
        warmup = hmc$warmup,
        refresh = hmc$refresh,
        control = list(
          adapt_delta = hmc$adapt_delta,
          max_treedepth = hmc$max_treedepth
        ),
        file = str_glue("output/brm-2-se-{cur_group()}")
      )
    )
  )
```

@@

```{r}
bf_2_f <- bf(
  val ~ 
    year * sex + year * age + f1_cw * sex + f1_cw * age + f1_cb + 
    (year * sex + year * age + f1_cw * sex + f1_cw * age | country) +
    (year * sex + year * age + f1_cw * sex + f1_cw * age | region),
  family = gaussian(), 
  unused = ~ cause
)

@@

bf_2_m <- bf(
  val ~ 
    year * sex + year * age + m1_cw * sex + m1_cw * age + m1_cb + 
    (year * sex + year * age + m1_cw * sex + m1_cw * age | country) +
    (year * sex + year * age + m1_cw * sex + m1_cw * age | region),
  family = gaussian(),
  unused = ~ cause
)
